---
title: "Day 5 Session 1"
format: 
  html:
    code-fold: true
    code-summary: "Show me the code!"
editor: visual
execute: 
  echo: true
  warning: false
---

-   Using warning: false can hide warning messages on render doc

-   Echo is to hide the code

-   Using code-fold: true and code-summary: "Show me the code!" will give the reader the option to show the code on a drop down button

```{r}
library(tidyverse)
```

## Explore Star Wars dataset

-   Look at the first 6 lines

    ```{r}
    head(starwars)
    ```

-   Find the dimensions

    ```{r}
    dim(starwars)
    ```

-   Make histogram of characters heights

    ```{r}
    ggplot(data = starwars, aes(x = height)) + geom_histogram(color = 'red', fill = "forestgreen")
    ```

-   Make a scatterplot of height vs weight

```{r}
ggplot(data = starwars, aes(x = height, y = mass, color = eye_color)) + geom_point() + labs(title = "Starwars characters height vs weight", x = "Height(cm)", y = "Weight (kg)")
```

## Calculate Summary statistics 

Use mean() function to find means.

Use sd() function to find standard deviation

```{r}
# Remove NA values by adding na.rm = TRUE in mean function
mean_height <- mean(starwars$height, na.rm = TRUE)
mean_height

```

Find and store the standard deviation of characters heights

```{r}
sd_height <- sd(starwars$height, na.rm =TRUE)
sd_height
```
